Simple repression draft

### 2020-06-04 doc/appendix_03_bayesian_inference.tex
add PPC figure to SI for unregulated promoters

With this, we are ready to write our full generative model as
\begin{equation}
\begin{split}
\ln k_i \sim \text{Normal}(-0.5, 2),
\\
\ln b \sim \text{Normal}(0.5, 1),
\\
m \sim \text{NBinom}(k_i, b).
\end{split}
\end{equation}
Section~\ref{section_04_bayesian_inference} in the main text details the
results of applying this inference to the single-cell mRNA counts data.

>>>>

With this, we are ready to write our full generative model as
\begin{equation}
\begin{split}
\ln k_i \sim \text{Normal}(-0.5, 2),
\\
\ln b \sim \text{Normal}(0.5, 1),
\\
m \sim \text{NBinom}(k_i, b).
\end{split}
\end{equation}
Section~\ref{section_04_bayesian_inference} in the main text details the
results of applying this inference to the single-cell mRNA counts data. There
we show the posterior distribution for the two parameters for different 
promoters. Figure~\ref{figS:ppc_unreg} shows the so-called posterior predictive
checks (see main text for explanation) for all 18 unregulated promoters shown
in the main text.

\begin{figure}[p]
\centering
\includegraphics{../figures/si/figS0X_ppc.pdf}
\caption{\textbf{Theory-data comparison of inference on unregulated promoters.}
Comparison of the inference (red shaded area) vs the experimental measurements
(black lines) for 18 different unregulated promoters with different mean mRNA
expression levels from Ref.~\cite{Jones2014}. Upper panels show the empirical
cumulative distribution function (ECDF), while the lower panels show the
differences with respect to the median of the posterior samples. White numbers
are the same as in Figure~\ref{fig1:means_cartoons} for cross comparison. The
predicted binding energies $\beta\Delta\varepsilon_p$ were obtained from the
energy matrix model in Ref.~\cite{Brewster2012}}
\label{figS:ppc_unreg}
\end{figure}
